Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-11-06 manuscript/paper-tycho.tex
Tycho regions-6 fits, srcutlog fits; Kepler tables
Running Tycho regions-6, Kepler regions-3 through pipeline
Cell to run srcutlog fits for Tycho
APLpy script to generate Tycho figure for manuscript
Move images/notes for Tycho RGB images to higher level
Script to generate damped FWHM tables for Kepler
Plots of param space, fix paper eta2=1 table
Fits for spectral index variation
Compute fits to harder X-ray tails to assess spectral index variation
Refactor PyXSPEC interfacing code to simplify adding fits etc
Notes on X-ray emission lines

% srcut constraint on diffusion
As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
flux, the synchrotron roll-off frequency may provide an independent observable
to estimate shock diffusion and is given by:
\begin{align} \label{eq:rolloff}
    \nu_{\mt{cut}} =
        &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
        \left(0.2657 \unit{erg^2\;G}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
        &\left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
\end{align}
In particular, this equation is independent of magnetic field $B$ for all
values of $\mu$ (but, recall that the specific electron energies associated
with $\eta_2$ will depend on $B$).

@@

% TODO final figure should be higher quality, use vector overlay if possible
\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
    }{
        \plotone{figures/f0-snr-inv.png}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \note[Aaron]{Inverted colors for draft only}
    \label{fig:snr}}
\end{figure}
% NOTE keep region # bolding updated to match displayed filaments

@@

\begin{table*}
    \scriptsize
    \centering
    \caption{Region spectra fit parameters\label{tab:spec}}
    \input{tab-spec.tex}
    \tablecomments{Absorbed power law fit parameters are photon index $\Gamma$
        and hydrogen column density $N_{\mt{H}}$.  Horizontal rules group
        individual regions into filaments.}
    \tablecomments{(DRAFT) Region 5 has unusually poor chi-squared due to a
        silicon line bump.  The 0.7--1 keV FWHM in Region 5 is $\abt 9\arcsec$
        and very poorly-fit, being close to not measurable.  In the next
        iteration of the data pipeline, I will cull the FWHMs by hand (Regions
        1--3, 5, 11--12, 18--19 will not have FWHMS at 0.7--1 keV); after bad
        FWHMs are removed, the spectral fits for Regions 5, 19 should improve.}
\end{table*}

>>>>

% srcut constraint on diffusion
As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
flux, the synchrotron roll-off frequency may provide an independent observable
to estimate shock diffusion and is given by:
\begin{align} \label{eq:rolloff}
    \nu_{\mt{cut}} =
        &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
        \left(100 \muG\right)
        \left(2657 \unit{erg^2}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
        &\left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
\end{align}
In particular, this equation is independent of magnetic field $B$ for all
values of $\mu$ (but, recall that the specific electron energies associated
with $\eta_2$ will depend on $B$).

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        %\includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
    }{
        %\plotone{figures/f0-snr-inv.png}
        \plotone{figures/snr.pdf}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \note[Aaron]{Inverted colors for draft only}
    \label{fig:snr}}
\end{figure}
% NOTE keep region # bolding updated to match displayed filaments

@@

\begin{table*}
    \scriptsize
    \centering
    \caption{Region spectra fit parameters\label{tab:spec}}
    \input{tab-spec.tex}
    \tablecomments{Absorbed power law fit parameters are photon index $\Gamma$
        and hydrogen column density $N_{\mt{H}}$.  Horizontal rules group
        individual regions into filaments.}
\end{table*}

\begin{table*}
    \scriptsize
    \centering
    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
    \input{suppl-spec-pt2.tex}
    \tablecomments{As described in text,
    we consider absorbed power law fits with lines fitted to two Gaussians
    (here characterized by equivalent width and line energy), or with lines
    manually excised.  See comments on Table~\ref{tab:spec}.}
\end{table*}
